\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format

\usepackage{amsmath}
\usepackage[hmargin = 2cm, vmargin = 2cm]{geometry}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\raggedbottom


\usepackage{xcolor}
\definecolor{charcoal}{RGB}{5, 5, 5}
\definecolor{paper}{RGB}{212, 212, 203}
\definecolor{forest}{RGB}{6, 26, 2}
\definecolor{strawberry}{RGB}{232, 70, 70}
\definecolor{tinged}{RGB}{247, 244, 240}
\definecolor{myblue}{RGB}{33, 97, 217}
\definecolor{mygreen}{RGB}{16, 133, 47}

\newcommand{\mypagecolor}{paper}
\pagecolor{paper} %% background
\color{charcoal} %% font

\begin{document}

\thispagestyle{empty}

\begin{center}
\textbf{\Large{Kat Matheson}} \\ \vspace{4pt}  438-526-7751 $\cdot$ g3.matheson@gmail.com $\cdot$ Montr\'eal, Qu\'{e}bec
\end{center}

\vspace{12pt}

\textbf{\large{Education}}

\small

\vspace{4pt}

\textbf{(2017) BMath: Mathematical Finance} \hfill \textbf{University of Waterloo}

\vspace{-8pt}
\begin{itemize}
\item Minor in Pure Mathematics.
\end{itemize}

\vspace{-4pt}

\textbf{(2019) MMath: Statistics} \hfill \textbf{University of Waterloo}

\vspace{-8pt}
\begin{itemize}
\item Thesis: On multiple random locations of stationary stochastic processes.
\end{itemize}

\vspace{-4pt}

\textbf{(2019- 2021) PhD: Applied Mathematics (incomplete)} \hfill \textbf{University of Waterloo}

\vspace{-8pt}
\begin{itemize}
\item Research topic: detecting, modeling and predicting self-similar patterns in data.
\end{itemize}

\vspace{-4pt}

\textbf{(Jan 2024 -- Present) BCs: Computer Science (Games Option)} \hfill \textbf{Concordia University}

\vspace{-8pt}
\begin{itemize}
\item Coursework in C\texttt{++}, Java, Python.
\end{itemize}

\vspace{12pt}

\textbf{\large{Skills}}
\small \vspace{-4pt}
\begin{itemize}
\item C\texttt{\#} (WPF), C\texttt{++}, R, Java, Python (Pandas, PySpark), SQL, Tableau, Jira, Perforce, Git, Linux.
\vspace{-4pt}
\item Bilingual in French \& English.
\vspace{-4pt}
\item Excellent \& rigorous attention to detail.
\end{itemize}

\vspace{12pt}

\textbf{\large{Employment}}
\small 

\vspace{8pt}

\textbf{Beenox, Tools Programming Intern} \hfill \textbf{Jan 2025 -- Aug 2025}
\begin{itemize}
\item Creating and maintaining features for C\texttt{\#} WPF tools used by the Call of Duty teams at large.
\vspace{-4pt}
\item Assisting users with issues, bugs and miscellaneous inquiries.
\end{itemize}

\vspace{4pt}

\textbf{Ubisoft, Game Intelligence Analyst} \hfill \textbf{Jan 2021 -- Mar 2023}
\vspace{-4pt}
\begin{itemize}
\item Game analytics: activity, retention \& monetization; balancing and user test analysis; survey design \& analysis.
\vspace{-14pt}
\item ETL building, maintenance, restructuring, automation and quality assurance with Spark SQL, PySpark, Tableau, Git/Perforce, and internal custom tools.
\vspace{-4pt}
\item Custom pipelines for rigorous statistical analyses in R.
\vspace{-4pt}
\item Collaborations done in Agile environment using Jira.
\vspace{-4pt}
\item Principal analyst on Rainbow Six: Extraction from date of hire up to launch, then on Rainbow Six: Siege.
\end{itemize}

\vspace{4pt}

\textbf{University of Waterloo, Sessional Lecturer} \hfill \textbf{Sept -- Dec 2020}
\vspace{-4pt}
\begin{itemize}
\item Teaching Calculus I for Honours Mathematics: delivering (in-person) lectures, developing lecture materials, creating and reviewing assignment, quiz and exam questions, helping students outside of class.
\end{itemize}

\vspace{4pt}

\textbf{University of Waterloo, Teaching Assistant} \hfill \textbf{Sept 2017 -- Aug 2020}
\vspace{-4pt}
\begin{itemize}
\item Delivering weekly tutorials (on R coding, practical examples), marking assignments and exams, proctoring, holding office hours  for undergraduate math courses.
\vspace{-4pt}
\item Head Teaching Assistant for 5 courses throughout 2017-2020: responsible for organizing and delegating tasks to the other teaching assistants.
\end{itemize}

\vspace{4pt}

\textbf{Self-Employed Tutor} \hfill \textbf{2008 -- 2020}
\vspace{-4pt}
\begin{itemize}
\item Private mathematics tutor for elementary, highschool, college and university students. Over 30 students taught, ranging from 4 months to upwards of 3 years each.
\end{itemize}


\end{document}
